%__________________________________________________________________________________
% @brief    LaTeX CV for Milos Atz
% NOTE: Many, many thanks and all credit for these materials go to Katy Huff, whose CV .tex file I borrowed and modified to make this document.

\documentclass[margin,line]{resume}
% \usepackage{bibentry}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
% \urlstyle{same}
% \usepackage{xspace}
%\textheight=10.75in

%__________________________________________________________________________________
\begin{document}
\name{\Large Milo\v{s} Ivo Atz \vspace{2mm}} 
\begin{resume}
% Contact Information
\section{\mysidestyle Contact\\Information}
    Nuclear Engineer
        \hfill mobile: (860) 918-6759 \\
    Argonne National Laboratory
        \hfill e-mail: matz [at] anl [dot] gov \\
    9700 South Cass Avenue, Building 208, Room A106
        \hfill website: \url{https://milosatz.github.io}\\
    Lemont, IL 60439 USA
% \hfill github: \url{https://github.com/MilosAtz}
% \hfill ORCID: 0000-0003-1928-9556
%__________________________________________________________________________________
%
% % Resume Objective
%\section{\mysidestyle Objective}
%Seeking research and teaching opportunities in nuclear engineering and scientific computation.
%
%__________________________________________________________________________________% 
%
% % Research Interests
%\section{\mysidestyle Research\\Interests}
%Advanced nuclear reactors and fuel cycles, multi-physics simulation, nuclear fuel cycle analysis, scientific computation.
%
%__________________________________________________________________________________

% Education
\section{\mysidestyle Ph.D.}
    \textbf{University of California, Berkeley}, 
    \textsc{Nuclear Engineering} \hfill 
    \textbf{Aug 2014 -- Sep 2019} \vspace{1mm} \\
    Dissertation: \textsl{Methodologies for the evaluation of nuclear waste management strategies and applications to advanced fuel cycles} \\
    Advisor: Professor Massimiliano Fratoni

\section{\mysidestyle M.S.}
    \textbf{University of California, Berkeley}, 
    \textsc{Nuclear Engineering} \hfill 
    \textbf{Aug 2014 -- May 2016} \vspace{1mm} \\
    Thesis: \textsl{Effect of initial enrichment and discharge burnup on the minimum critical mass of far-field depositions of fissile material from LWR spent fuel} \\
    Advisor: Professor Joonhong Ahn

\section{\mysidestyle B.S.}
    \textbf{University of Connecticut}, 
    \textsc{Chemical Engineering} \hfill 
    \textbf{Aug 2010 -- May 2014} \vspace{1 mm} \\
    Thesis: \textsl{Mechanism of insulin aggregation: Applied to Alzheimer’s disease} \\
    Advisor: Professor Mu-Ping Nieh \\
%__________________________________________________________________________________
% Research Experience
\section{\mysidestyle Research \\ Experience}

\textbf{Argonne National Laboratory}, Lemont, IL \hfill
    \textbf{Sep 2020 -- present} \\
\textsl{Nuclear Engineer, Nuclear Science and Engineering Division} \\
Continued development of DASSH subchannel TH software to calculate core-wide temperatures and inform orificing strategies in support of the Versatile Test Reactor core design. Engage in research and development activities related to advanced reactor core design \& analysis and fuel cycle \& waste management planning.

\textbf{Argonne National Laboratory}, Lemont, IL \hfill
    \textbf{Sep 2019 -- Aug 2020} \\
\textsl{Postdoctoral Appointee, Nuclear Science and Engineering Division} \\
Development of DASSH subchannel TH software in support of the Versatile Test Reactor core design.

\textbf{University of California, Berkeley}, Berkeley, CA \hfill 
    \textbf{Aug 2014 -- Sep 2019 } \\
\textsl{Graduate Research Assistant, Nuclear Waste Management Group} \\
Implemented analysis tools to study the nuclear fuel cycle and waste management by leveraging the data produced in the DOE Fuel Cycle Evaluation and Screening study.

\textbf{University of Connecticut}, Storrs, CT \hfill 
    \textbf{Sep 2012 -- May 2014} \\
\textsl{Undergraduate Research Assistant, Self-Assembled Functional Nanomaterials Lab} \\
Studied reversibility of insulin dimerization as model for potential reversal of Alzheimer's disease.

\textbf{Idaho National Laboratory}, Idaho Falls, ID \hfill 
    \textbf{Jun -- Aug 2013} \\
\textsl{SULI Research Intern, Energy Resource Recovery and Sustainability Department} \\
Developed thermal models for biofuel feedstock degradation and cold crucible induction melters.

\textbf{UTC Power}, South Windsor, CT \hfill 
    \textbf{Jun -- Aug 2012} \\
\textsl{Cell Stack Research Intern} \\
Studied subscale fuel cells to assess feasibility of replacing purge gas with cheaper alternative. Performed thermal conductivity tests on fuel cell components to correct model correlations.\\

%__________________________________________________________________________________
% Honors and Awards
\section{\mysidestyle Honors and\\Awards}
Impact Argonne Award (shared) for contributions to VTR CD-1 milestone \hfill \textbf{November 2020}\vspace{.5mm} \\
First place, MeV School final team project presentation \hfill \textbf{Summer 2020}\vspace{.5mm} \\
UC Berkeley Nuclear Engineering Joonhong Ahn Award \hfill \textbf{Spring 2019}\vspace{.5mm} \\
Roy G. Post Nuclear Waste Management Graduate Scholarship \hfill \textbf{Spring 2019}\vspace{.5mm} \\
National Science Foundation Graduate Research Fellowship \hfill \textbf{2015 -- 2019}\vspace{.5mm} \\
First place, Nuclear Innovation Bootcamp \hfill \textbf{Summer 2016}\vspace{.5mm} \\
UC Berkeley Nuclear Engineering Thomas Pigford Award \hfill \textbf{Spring 2016}\vspace{.5mm} \\	
Nuclear Regulatory Commission Graduate Fellowship \hfill \textbf{Spring 2015}\vspace{.5mm} \\
United Technologies Corporation Engineering Scholarship \hfill \textbf{2013 -- 2014}\vspace{.5mm} \\
Honorable Mention (x2), Idaho National Laboratory Intern Poster Competition \hfill \textbf{Summer 2013}\vspace{.5mm} \\
University of Connecticut Academic Excellence Scholarship \hfill \textbf{2010 -- 2014} \\

%__________________________________________________________________________________
% RESEARCH CONTRIBUTIONS
% Journal Papers
\section{\mysidestyle Journal\\Publications}
\begin{bibenum}

    \item A. Kasam-Griffith, \textbf{M. Atz}, T. Fei, Z. Zhong, M. Jarrett, F. Heidet. ``VTR Core Design for Flexible Operations''. \textbf{Nuclear Science and Engineering}. Submitted.

    % \item \textbf{M. Atz}, M. Fratoni. ``Waste management strategies for advanced fuel cycles''. In preparation.

    \item \textbf{M. Atz}, A. Salazar, F. Hirano, M. Fratoni, J. Ahn. ``Assessment of the potential for criticality in the far field of a used nuclear fuel repository''. \textbf{Annals of Nuclear Energy} 124, pp 28-38, February 2019. \href{https://doi.org/10.1016/j.anucene.2018.09.028}{DOI}.
    
\end{bibenum}
%__________________________________________________________________________________
% Conference proceedings
\section{\mysidestyle Conference\\Proceedings}
\begin{bibenum}

    \item \textbf{M. Atz}, M. A. Smith, F. Heidet. ``DASSH: Software for ducted assembly thermal hydraulics calculations''. \textbf{Transactions of the American Nuclear Society} 123 pp. 1673-1676, November 2020.

    \item \textbf{M. Atz}, M. Fratoni. ``Impact of interim storage on repository design options''. Paper 27261. \textbf{International High-Level Radioactive Waste Management Conference (IHLRWM 2019)}, Knoxville, TN, April 2019.
    
    \item \textbf{M. Atz}, M. Fratoni. ``A Python Package for Fuel Cycle and Waste Management Analysis''. Paper 19545. \textbf{Proceedings of the Waste Management Symposium}, Phoenix, AZ, March 2019. \href{http://amz.xcdsystem.com/A464D2CF-E476-F46B-841E415B85C431CC_finalpapers_2019/FinalPaper_19545_0121045947.pdf}{URL}.
    
    \item \textbf{M. Atz}, M. Fratoni. ``Impact of partitioning and transmutation on the back end of the fuel cycle''. \textbf{Proceedings of the OECD 15th International Exchange Meeting on Partitioning and Transmutation}, Manchester, UK, October 2018.
    
    \item A. Salazar, \textbf{M. Atz}, X. Liu, M. Fratoni. ``The Criticality Safety Studies of Joonhong Ahn''. \textbf{Transactions of the American Nuclear Society}, Vol. 116, San Francisco, CA, June 11-15, 2017.

    \item \textbf{M. Atz}, X. Liu, M. Fratoni, J. Ahn. ``Material composition effects on far-field deposition minimum critical mass''. \textbf{International High-Level Radioactive Waste Management Conference (IHLRWM 2017)}, Charlotte, NC, April 9-13, 2017. \href{https://www.researchgate.net/profile/Milos-Atz/publication/328150158_Material_composition_effects_on_far-field_deposition_minimum_critical_mass/links/5bbbd7bf299bf1049b75d9bf/Material-composition-effects-on-far-field-deposition-minimum-critical-mass.pdf}{URL}.

    \item \textbf{M. Atz}, X. Liu, M. Fratoni, J. Ahn. ``Evaluation of minimum critical mass to inform performance requirement of partitioning and transmutation to eliminate criticality risk in a geologic repository''. \textbf{Proceedings of the OECD 14th International Exchange Meeting on Partitioning and Transmutation}, San Diego, CA, October 2016. pp. 354-364. \href{https://www.oecd-nea.org/science/docs/2017/nsc-r2017-3.pdf}{URL}.

\end{bibenum}
%__________________________________________________________________________________
% Technical Reports
\section{\mysidestyle Technical\\Reports}

\begin{bibenum}

    \item \textbf{M. Atz}, M. A. Smith, F. Heidet. ``Ducted Assembly Steady-State Heat Transfer Software (DASSH) - User Guide''. ANL/NSE-21/34 (2021). \href{https://www.osti.gov/biblio/1812216-ducted-assembly-steady-state-heat-transfer-software-dassh-user-guide}{URL}.

    \item \textbf{M. Atz}, M. A. Smith, F. Heidet. ``Ducted Assembly Steady-State Heat Transfer Software (DASSH) - Theory Manual''. ANL/NSE-21/33 (2021). \href{https://www.osti.gov/biblio/1813446-ducted-assembly-steady-state-heat-transfer-software-dassh-theory-manual}{URL}.
    
    \item \textbf{M. Atz}, B. Feng. ``Generic Activities and Milestones for Deploying Advanced Reactor Spent Fuel Management Facilities''. ANL/NSE-21/28 (2021).
    
    \item A. G. Nelson, A. A. Kasam-Griffith, \textbf{M. I. Atz}, F. Heidet. ``Performance of HALEU and HEU-Fueled Nuclear Thermal Propulsion Reactors''. ANL/NSE-20/55 (2020).
    
    \item A. Kasam-Griffith, M. Jarrett, \textbf{M. Atz}, G. Aliberti. ``Comparative analysis of the reference VTR conceptual core design''. ECAR-5119 (2020).

    \item A. G. Nelson, M. A. Smith, \textbf{M. I. Atz}, F. Heidet. ``Argonne Reactor Computation Code Verification -- Phase 1 Achievements''. ANL-VTR-58 (2020).

    \item A. Salazar, \textbf{M. Atz}, M. Fratoni. ``Criticality Safety for Geological Disposal of Used Nuclear Fuel''. Summary Report for the FY2016 for JAEA-UCBNE Collaboration (Area 2) UCB-NE-5157 (2017).
    
    \item X. Liu, A. Salazar, \textbf{M. Atz}, M. Fratoni, J. Ahn. ``Preliminary Criticality Safety Assessment for Direct Disposal of Spent Nuclear
	Fuels''. Summary Report for the FY2015 for JAEA-UCBNE Collaboration (Area 2) UCB-NE-5153 (2016).
	
	\item X. Liu, A. Salazar, \textbf{M. Atz}, M. Fratoni, J. Ahn. ``Criticality Safety for Geological disposal of Fukushima Damaged Fuels''. Summary Report for the FY2015 for JAEA-UCBNE Collaboration (Area 1) UCB-NE-5152 (2016).

    \item J. Ahn, X. Liu, \textbf{M. Atz}. ``Preliminary Criticality Safety Assessment for Direct Disposal of Spent Nuclear Fuels''. Summary Report for the FY2015 for JAEA-UCBNE Collaboration (Area 2) UCB-NE-5148 (2015).

\end{bibenum}
%__________________________________________________________________________________
% Theses
\section{\mysidestyle Theses\\}
\begin{bibenum}
    
    \item \textbf{M. Atz}. ``Methodologies for the evaluation of nuclear waste management strategies and applications to advanced fuel cycles''. PhD Dissertation, UC Berkeley (2019). \href{http://search.proquest.com/openview/bf6b3e374367e5f1164c84d313c6e783/1?pq-origsite=gscholar&cbl=18750&diss=y}{URL}.

    \item \textbf{M. Atz}. ``Effect of initial enrichment and discharge burnup on the minimum critical mass of far-field depositions of fissile material from LWR spent fuel''. Master's Report (Plan II) UCB-NE-5155 (2016).

    \item \textbf{M. Atz}, M. Li, G. Belfort, M.P. Nieh. ``Mechanism of insulin aggregation: Applied to Alzheimer’s disease''. University of Connecticut Honors Scholar Thesis, Paper 378, Chemical Engineering (2014). \href{https://opencommons.uconn.edu/cgi/viewcontent.cgi?referer=&httpsredir=1&article=1386&context=srhonors_theses}{URL}.
    
\end{bibenum}
%__________________________________________________________________________________
% Posters
\section{\mysidestyle Posters}
\begin{bibenum}

    \item K. Shield, \textbf{M. Atz}. ``Nuclear Energy and Environmental Justice: As Bad as we Think?'' \textbf{National Science Policy Symposium}, New York, NY, November 2018.
    
    \item \textbf{M. Atz}, M.P. Nieh, M. Li. ``Understanding the early stage of insulin aggregation; applied to Alzheimer’s disease''. \textbf{American Institute of Chemical Engineers Regional Student Conference}, Storrs, CT (2014).

    \item \textbf{M. Atz}, M.P. Nieh, M. Li. ``Insulin as a Model System for Beta-Amyloid Protein Aggregation Reversibility''. \textbf{American Institute of Chemical Engineers National Student Conference}, San Francisco, CA (2013).

    \item \textbf{M. Atz}, M. Plummer, I. Bonner, W. Smith. ``Mathematical Simulation of Biodegradation in Corn Stover''. Idaho National Laboratory Intern Poster Competition (2013).

\end{bibenum}
%__________________________________________________________________________________
% Other writing
\section{\mysidestyle Other\\Writing}
\begin{bibenum}

    \item F. Heidet, \textbf{M. Atz}. ``Why Crypto Mining Needs Nuclear Power''. CoinDesk (2021). \href{https://www.coindesk.com/policy/2021/10/13/why-crypto-mining-needs-nuclear-power/}{URL}.
    
    \item \textbf{M. Atz}. ``Understanding the Nuances of Nuclear Waste''. Medium, Berkeley Nuclear Engineering (2017). \href{https://medium.com/berkeley-nuclear-engineering/understanding-the-nuances-of-nuclear-waste-5c123ba4211f}{URL}.
    
    \item \textbf{M. Atz}. ``Pioneering the future of nuclear energy innovation''. Berkeley Energy \& Resources Collaborative (2016). \href{http://berc.berkeley.edu/pioneering-future-nuclear-energy-innovation/}{URL}.
\end{bibenum}

\vspace{8mm}
%__________________________________________________________________________________
% Invited lectures
\section{\mysidestyle Invited\\Talks}
\textbf{Santa Clara University} Physics Department, \textsl{Seminar} \hfill \textbf{Jun 1, 2020}\\
\textbf{NNSA University Program Review}, Raleigh, NC, \textsl{NSSC Affiliate} \hfill \textbf{Jun 4-6, 2019}\\
\textbf{NSSC MSIM Schubert Review}, Berkeley, CA, \textsl{NSSC Affiliate} \hfill \textbf{Apr 23, 2019}\\

%__________________________________________________________________________________
% Teaching Experience
\section{\mysidestyle Teaching\\Experience}

% \textbf{University of California, Berkeley}, \textsc{Dept. of Nuclear Engineering} \\
\textbf{University of California, Berkeley}, \textsc{Dept. of Nuclear Engineering}\\
Course organizer, \textsl{NE290E, Environmental Aspects of Nuclear Energy}
    \hfill \textbf{Spring 2019} \\
Teaching Assistant, \textsl{NE124, Radioactive Waste Management} 
    \hfill \textbf{Spring 2016} \\
Teaching Assistant, \textsl{NE290E, Environmental Aspects of Nuclear Engineering} \hfill \textbf{Fall 2015}\\
\vspace{0mm}\\
% \textbf{Guest lectures} \\
\textbf{Guest lectures} \\
% \textbf{University of California, Berkeley}, \textsc{Dept. of Nuclear Engineering}\\
\textsl{NE124, Radioactive Waste Management}
    \begin{itemize} %\vspace{-8mm}
        \item Repository thermal management \hfill \textbf{Apr 30, 2019}\vspace{-1mm}
        \item Criticality safety studies at UC Berkeley \hfill \textbf{Apr 14, 2017}
    \end{itemize} \vspace{-4mm}
\textsl{NE100, Introduction to Nuclear Engineering}
    \begin{itemize}
        \item Nuclear fuel cycle mass balances, radiation dose conversions \hfill \textbf{Apr 24 \& 26, 2018} \\
    \end{itemize}
% 
% \textbf{University of California, Berkeley}, \textsc{Dept. of Nuclear Engineering} 
%     \hfill \textbf{Apr 24 \& 26, 2018}
%     \textsl{NE100, Introduction to Nuclear Engineering} \\
%     Nuclear fuel cycle mass balances, radiation dose conversions\\
% \vspace{0mm} \\ 
% \textbf{University of California, Berkeley}, \textsc{Dept. of Nuclear Engineering} \hfill \textbf{Apr 14, 2017} \\
%     \textsl{NE124, Radioactive Waste Management} \\
%     Criticality Safety Studies at UC Berkeley \\
%__________________________________________________________________________________

% Volunteering and service
\section{\mysidestyle Volunteering\\and Service}
Reviewer, Nuclear Engineering and Technology \\
Member, EGS DEI Council
    \hfill \textbf{Nov 2020 -- present} \\
Member, MeV School Scientific Secretariat
    \hfill \textbf{Summer 2021} \\
Vice President, Postdoctoral Society of Argonne
    \hfill \textbf{Jan 2020 -- Dec 2020} \\
Workshop Leader, \href{https://www.earthactioninitiative.org/}{Earth Action Initiative}
    \hfill \textbf{Spring 2018, Spring 2019} \\
UC Berkeley Nuclear Engineering Colloquia Review Committee 
    \hfill \textbf{Fall 2017 -– Spring 2018} \\
Nuclear Innovation Bootcamp Planning Committee	
    \hfill \textbf{Spring 2017 –- Summer 2018} \\
Summer Session Volunteer, The Painted Turtle
    \hfill \textbf{Summer 2017, 2018} \\
Executive Committee, Nuclear Environmental Outreach Group
    \hfill \textbf{Fall 2016 -– Fall 2017} \\
Vice President, UConn Engineering Ambassadors
    \hfill \textbf{Fall 2013 –- Spring 2014} \\
Member, UConn Engineering Ambassadors
    \hfill \textbf{Fall 2012 –- Spring 2014} \\
UConn Engineering Dean Search Committee
    \hfill \textbf{Fall 2013} \\
Representative, UConn Chemical Engineering ABET Review
    \hfill \textbf{Fall 2013} \\
Student Interviewer, UConn Chemical Engineering Faculty Search
    \hfill \textbf{Spring 2013} \\
Submitted \href{https://www.cga.ct.gov/2013/FINdata/Tmy/2013SB-00840-R000304-Milos\%20Atz,\%20Student,\%20UConn-TMY.PDF}{testimony} in support of CT Senate Bill no. 840
    \hfill \textbf{Spring 2013} \\ %

% https://www.cga.ct.gov/2013/FINdata/Tmy/2013SB-00840-R000304-Milos%20Atz,%20Student,%20UConn-TMY.PDF

% Produced video for Nuclear Engineering Student Advocacy and Awareness Competition (2nd place) \hfill \textbf{2016} \\


\end{resume}

\end{document} 

%__________________________________________________________________________________

% Computer skills? Professional and Student organizations?

%__________________________________________________________________________________